Centralizers of higher enveloping algebras and their large $N$ limits

### 2019-05-07 frame.tex

When $n=1$ and $\cC$ is chain complexes over the field $k$, 
then $\Mod^{E_1}_A(\cC)$ is equivalent to $A-A$-bimodules and hence ${\frak Z}_{E_1}(f) \simeq \HH^*(A,B_f)$,
where $B_f$ denotes $B$ viewed as an $A-A$-bimodule via the map~$f$.

@@

Let $\fg$ be a dg Lie algebra, let $B$ be an $E_n$ algebra, and let $f: \UU_n \fg \to B$ be a map of $E_n$ algebras.
Then the results of the preceding section imply
\begin{align*}
{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B_f) \\
&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}}(\UU_n \fg, B_f)
\end{align*}
where 
\begin{itemize}
\item $B_f$ denotes the object in $\Mod^{E_n}_{\UU_n}$ or, equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ determined by~$f$,
\item ${\rm Mor}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B)$ denotes the classifying object for maps from $\UU_n$ to $B_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n}$ (i.e., an internal mapping object),
\item and ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)$ denotes the classifying object for maps from ${\UU_n}$ to $B$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n}$.
\end{itemize}
Observe now that $\int_{S^{n-1}}\UU_n$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
This is because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.
Using the canonical inclusion $i: U\fg \to U(\fg \otimes k[\epsilon_{n-1}])$,
we find
\[
k \otimes_{U\fg} U(\fg \otimes k[\epsilon_{n-1}]) \simeq \Sym(\fg[1-n]).
\]
Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules.
Base change thus implies
\[
{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)  \simeq {\rm Mor}_{U\fg} (k, B_f).
\]
The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.

\brian{do you like this example?}
\begin{eg}\label{eg: TT}
Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
The Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$. 
On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning 
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR$.
In particular, the factorization homology of the derived center along the closed manifold $S^1$ can be computed as
\[
\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
\]
where $\epsilon$ is a formal variable of degree $+1$. 
\brian{let's talk about this.}
\end{eg}

@@

Note that for two algebras $B$ and $B'$,
\[
\Cyc_*(B) \oplus \Cyc_*(B') \simeq \Cyc_*(B \times B') .
\] 
The corresponding statement for ordinary Hochschild homology is induced by the projections $B \leftarrow B \times B' \to B'$, and any map of algebras that induces a quasi-isomorphism on Hochschild homology induces one on cyclic homology as well.
See, for instance, 2.2.12 of \cite{LodayCyclic}. 
Hence, for any finite collection of disjoint opens $U_1$, \dots, $U_k$, 
we have
\[
\cC_A(U_1 \sqcup \cdots \sqcup U_k) \simeq \cC_A(U_1) \oplus \cdots \oplus \cC_A(U_k).
\]
(In this sense $\cC_A$ behaves like a cosheaf, up to quasi-isomorphism. 
\owen{Does cyclic homology preserve filtered colimits? If so, I think $\cC_A$ may be a homotopy cosheaf.}
\brian{Yes, see E.2.1.1 of \cite{LodayCyclic} on p. 59.}
This property underlies the following claim.

@@

%\section{Proof of Theorem~\ref{thm: large N}}

>>>>

When $n=1$ and $\cC$ is chain complexes over the field $k$, 
then $\Mod^{E_1}_A(\cC)$ is equivalent to $A-A$-bimodules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
where $B_f$ denotes $B$ viewed as an $A-A$-bimodule via the map~$f$.

@@

Let $\fg$ be a dg Lie algebra, let $B$ be an $E_n$ algebra, and let $f: \UU_n \fg \to B$ be a map of $E_n$ algebras.
Then the results of the preceding section imply
\begin{align*}
{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B_f) \\
&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}}(\UU_n \fg, B_f)
\end{align*}
where 
\begin{itemize}
\item $B_f$ denotes the object in $\Mod^{E_n}_{\UU_n}$ or, equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ determined by~$f$,
\item ${\rm Mor}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B)$ denotes the classifying object for maps from $\UU_n$ to $B_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n}$ (i.e., an internal mapping object),
\item and ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)$ denotes the classifying object for maps from ${\UU_n}$ to $B$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n}$.
\end{itemize}
Observe now that $\int_{S^{n-1}}\UU_n$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
This is because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.
Using the canonical inclusion $i: U\fg \to U(\fg \otimes k[\epsilon_{n-1}])$,
we find
\[
k \otimes_{U\fg} U(\fg \otimes k[\epsilon_{n-1}]) \simeq \Sym(\fg[1-n]).
\]
Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules.
Base change thus implies that we have an equivalence
\[
{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)  \simeq {\rm Mor}_{U\fg} (k, B_f)
\]
of underlying chain complexes.
(That is, we have an equivalence after applying forgetful functors.)
The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.

\brian{do you like this example?}
\begin{eg}\label{eg: TT}
Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
The Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$. 
On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning 
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR$.
In particular, the factorization homology of the derived center along the closed manifold $S^1$ can be computed as
\[
\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
\]
where $\epsilon$ is a formal variable of degree~$1$. 
\brian{We should compare with Tamarkin-Tsygan's noncommutative claculus (cf. section 2.6).
We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
\end{eg}

@@

Note that for two algebras $B$ and $B'$,
\[
\Cyc_*(B) \oplus \Cyc_*(B') \simeq \Cyc_*(B \times B') .
\] 
The corresponding statement for ordinary Hochschild homology is induced by the projections $B \leftarrow B \times B' \to B'$, and any map of algebras that induces a quasi-isomorphism on Hochschild homology induces one on cyclic homology as well.
(See, for instance, \S2.2.12 of \cite{LodayCyclic}.)
Hence, for any finite collection of disjoint opens $U_1$, \dots, $U_k$, 
we have
\[
\cC_A(U_1 \sqcup \cdots \sqcup U_k) \simeq \cC_A(U_1) \oplus \cdots \oplus \cC_A(U_k).
\]
Moreover, for any nested sequence of inclusions $V_1 \subset V_2 \subset \cdots$ with $V = \bigcup_i V_i$,
there is a quasi-isomorphism
\[
{\rm hocolim}(\cC_A(V_1) \to \cC_A(V_2) \to \cdots) \simeq \cC_A(V).
\]
(See E.2.1.1 of \cite{LodayCyclic}.)
In this sense $\cC_A$ behaves like a cosheaf, up to quasi-isomorphism. 
This property underlies the following claim.

@@

\section{\owen{A stub about a twisted version of LQT}}

\owen{Brian and I will later insert an expansion of the following.}

Let $\chi \in \Cyc^m(A)$ is a cyclic cocycle of degree $m$. 
Then $\chi$ determines a central extension $\cC(A)_\chi$ of $\Cyc_*(A)[1]$ as an abelian Lie algebra (cf. Heisenberg Lie algebras),
but $\chi$ also maps to Lie algebra cochains $\clies(\gl_N(A))$ for every $N$ via the LQT map,
and hence determines a central extension $\gl_N(A)_\chi$ of $\gl_N(A)$ as well.
There is thus a $\chi$-twisted version of the LQT map
\[
\lqt_\chi: \Sym(\cC(A)_\chi) \to \cliels(\gl_N(A)_\chi)
\]
which is a quasi-isomorphism in the large $N$ limit.

This induces $\chi$-twisted versions of all our enveloping $E_n$ algebra theorems (in large $N$ limit).

%We briefly remark on a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
%For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A)$ be a cyclic {\em cocycle} of degree $m$.
%Consider for each open $U \subset \RR^n$ the cochain complex
%\[
%\Tilde{\cC}_{A,\chi} (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
%\]
%where $K$ is a formal parameter of degree $-m+n+1$.
%Also, $\d_{\rm Cyc}$ is the cyclic differential and $\chi$ is defined on $m$-chains by the pairing between cyclic chains and cochains, together with integration along $U$:
%\[
%\chi ((a_1 \otimes \alpha_1) \tensor \cdots \tensor (a_m \otimes \alpha_m)) = \int_U \<\chi, a_1 \tensor \cdots \tensor a_m\> \alpha_1 \wedge \cdots \wedge \alpha_m.
%\]
%The differential is extended to the entire cochain complex by the graded Leibniz rule. 
%By similar arguments as above, the assignment $U \subset \Tilde{\cC}_{A, \chi}$ is a precosheaf of cochain complexes and $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ is a prefactorization algebra. 
%As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{\CC}[m-n-1]$, where $\ul{\CC}$ is the constant precosheaf, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$. 
%These types of twisted \brian{what to say? check my degrees!}
%
